Collaborative Visual Analysis on the Web with RCloud

### 2015-06-25 conclusion.tex
fixed spelling errors

\section{Conclusions and Future Work}
We designed a prototype environment for exploration, sharing,
presentation, and publishing.  This study has provided a step toward
practical ``DevOps for data science'' and reproducible, publishable
experiments.

RCloud has become a valid avenue for easy deployment of visualizations
and interactive exploration tools inside our organization.  We found
that features for sharing and publishing were eagerly adopted.
Features for single-user data exploration, on the other hand, competed
with existing mature tools, and were not accepted as readily.  In
future work, we hope to study and to understand the degree to which
this reluctance is caused by bad design decisions on our part, and how
much comes from ``mere'' change aversion.

We still firmly believe that the current biggest barrier to the
adoption of visual analytics is in software infrastructure.
Just like structuring visualization software around
simple but composable parts is a successful approach (like Vega, ggplot and the grammar of
graphics), it is intriguing to consider what systems are
possible if this philosophy were carried over to the 
broader requirements of interactive analysis.

>>>>

\section{Conclusions and Future Work}
We designed and deployed a prototype environment for visual analytics
exploration, sharing, presentation, and publishing. It is a step toward
practical ``DevOps for data science'' and reproducible, publishable data
science experiments.

RCloud was accepted as a platform for easy deployment of visualizations
and interactive exploration tools inside our organization.  
Sharing and publishing were eagerly adopted.
Features for single-user data exploration, on the other hand, that
compete with existing mature tools, were not readily accepted.
In future work, we hope to study and to understand the degree to which
this reluctance is caused by bad design decisions on our part, and how
much comes from ``mere'' change aversion. It is also clear we need
need better ways to manage the persistence of workbooks and to cope
with potential information overload.

We find much evidence that the biggest barrier to the adoption of
visual analytics is inadequate software infrastructure.
Just as structuring visualization software around simple,
composable parts is highly successful (exemplified by
Grammar of Graphics approaches like Vega and ggplot)
it is intriguing to consider what systems will be
possible when this philosophy is extended to the
broader requirements of interactive analysis.
